\section{Conclusions}
\label{sec:conclusion}
In summary, the Similarity Powered Pairwise Amplifier Network (SPPAN)
model we proposed in this article shows promising results in
predicting click-through rate (CTR) in a very sparse CTR data set. It
utilizes the pairwise ratio similarity information that embedded in
the data set, and its model complexity is automatically adjusted
according to the sparsity of the data set. Comparing with several
matrix factorization based recommendation methods, our evaluation
experiment results show that this model can substantially improving
the performance of the recommendation system in extreme sparse
situations. It has also been shown that the training process of the
SPPAN model can be easily implemented in a paralleled version through
map-reduce, which makes the model can handle even bigger data set
efficiently.

Since all evaluation experiments in this paper were performed on a
click-through rate data set, we must observe that more experimental
evaluations of the proposed SPPAN model should be performed in the
future in order to make a more comprehensive conclusion of the
performance of the model. In fact, out next plan is to apply the SPPAN
model on other sparse data sets from different domains so that we
could confirm if the {\it Homogeneous Amplifying Effect} described in
Section \ref{sec:model_intuition} is valid only in online
advertisement traffic data or can be generalized in other
areas. Moreover, the experiment result in the present paper only shows
the advantages of the SPPAN model in a situation with a certain
sparsity level. A sensitivity analysis about the effect of the
sparsity on the model's performance would help us to decide when to
use SPPAN model instead of other approaches.
